Think deep for reef resilience

### 2025-09-11 paper/paper_draft.qmd
Proof read of the paper discussion
9202 words with figure/table captions
7619 without

---
title: Think deep for reef resilience
author:
  - name: Benjamin Grier
    email: grierben777@gmail.com
    affiliations:
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          state: QLD
    attributes:
        corresponding: true
  - name: Takuya Iwanaga
    email: t.iwanaga@aims.gov.au
    affiliations:
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          city: Cape Cleveland
          state: QLD
    attributes:
        corresponding: true
abstract: |
    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress events.
    Understanding drivers behind reef resilience to climate impacts is critical for conservation
    planning and intervention strategies. A scenario-based population modelling approach was
    adopted with larval connectivity dynamics, thermal adaptation, and environmental factors
    to assess coral reef resilience across GBR locations under future climate projections.
    Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
    we analysed reef coral cover time series and the ability of reefs to maintain positive carbonate
    production budgets under future conditions. Contrary to expectations, larval connectivity
    patterns did not correlate with increases in maintenance of positive carbonate budgets.
    Instead, reef depth emerged as the primary predictor of cover-time series resilience and
    maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
    refugia that reduce bleaching impacts. Interaction between reef depth and incoming 
    connectivity was found to influence reef temporal behaviour. Our findings suggest that 
    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current intervention
    practices that primarily target easily accessible sites in the 1-10m depth range. These results have 
    important implications for reef management, indicating that depth refugia should be 
    prioritized for further consideration in conservation planning alongside connectivity 
    considerations to maximize coral survival under continuing climate change.
keywords:
  - Coral reef
  - Climate change
  - Ecosystem resilience
  - Reef depth
  - Reef connectivity
date: last-modified
format:
  elsevier-docx:
    journal:
      name: Journal Name
      formatting: preprint
      cite-style: authoryear
bibliography: references.bib
engine: julia
crossref:
  custom:
  - kind: float
    reference-prefix: SFigure
    key: sfig
  custom:
  - kind: float
    reference-prefix: STable
    key: stbl
editor:
  markdown:
    wrap: 92
    canonical: true
---

@@

Across bioregions there were no consistent patterns between reef clusters in mean DHW values
(@sfig-access-esm1-5-bioregion-dhwmean), Log-10 weighted incoming connectivity
(@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength
(@sfig-access-esm1-5-bioregion-outoingconn), Log-10 source-to-sink connectivity ratio
(@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability
(@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
cover cluster have lower Log-10 carrying capacity values than reefs in other clusters
(@sfig-access-esm1-5-bioregion-carrying-capacity).

@@

Reef median depth had a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
@sfig-access-esm1-5-mean-carb-budget; @sfig-access-esm1-5-carb-budget-corr). Unsurprisingly,
the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as
does the Spearman's correlation (@sfig-access-esm1-5-carb-budget-corr). Decreasing
correlation levels are likely due to an increasing number of reefs being unable to maintain
coral cover above $\theta_0$ as it is increased, with the distribution of years above
threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In
contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no
correlation with the number of years a reef maintains cover above the required thresholds
(@fig-access-esm1-5-carb-budget-corr).

@@

Reefs in different temporal clusters largely do not differ in mean modelled DHW levels
experienced and exhibit overall similar DHW time series. While these reefs experience
similar magnitude DHWs based on SST, the proportion of the reefs' coral population impacted
by heat stress events depends on reef depth. Reefs at deeper depths are likely to be
clustered into High cover clusters. Reefs at shallow depths experience no, or few, years
with coral cover exceeding levels likely required to maintain positive carbonate budgets.
Movement of shallow reefs towards negative carbonate budgets in the future may contribute to
phase shifts in reef dominant CaCO~3~ production. Shifting from coral driven to encrusting
algae driven production, or to bioerosion dominated systems with rapid erosion of physical
reef frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to
maintain coral driven CaCO~3~ production and accumulation into the future for longer. Our
results suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m),
depth contributes greatly to reef resilience and the ability of the reef to maintain
positive carbonate budgets under future conditions. Spatially our results indicate that
positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth levels were
concentrated in the Far Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn
management areas (@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far
Northern management area were exposed to lower mean DHW levels than other reefs under
ACCESS-ESM1-5 (@sfig-mean-dhw-map). Similar spatial patterns were observed across GCMs for
reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do not
interpret these spatial findings as accurate predictions of future resilience due to high
uncertainty in input data, particularly depth and connectivity. While similar findings have
been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific [@bridge2014]
regions, depth refugia analyses have often focussed on the potential of mesophotic reefs (\>
30m deep) as thermal refugia [@bongaerts2010; @holstein2015; @semmler2017]. In contrast,
Venegas et al. [-@venegas2019] found no association between depth and the alleviation of
heat stress across a range of shallow reefs in the Pacific.

These findings support the hypothesis that reefs at greater depths will exhibit
characteristics of refugia and more prolonged structural resilience under climate change
compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
recruitment capacity of shallow reefs. A caveat to these depth-resilience findings is the
quality of the bathymetry data used to calculate median reef depth. As detailed previously,
estimates of median reef depth are derived from satellite imagery (at $10m^2$ resolution)
which can be subject to high degrees of uncertainty, both in terms of the estimated depth at
for each pixel as well as their alignment to the established GBRMPA reef outlines.
Additionally, we do not incorporate the light-based decreases in coral growth rates as depth
increases [@baker1975; @huston1985; @ruiz-diaz2022].

Current reef restoration and intervention efforts on the GBR, such as deployment of coral
seeding, fragment devices and Crown of Thorns Starfish control, target reefs with suitable
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
no explicit justifications for this depth range, intervention depth is likely constrained by
snorkelling and diving deployment and monitoring logistical accessibility, visual
identification of sites from the surface, in combination with tourism return value. Our
results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
reefs), 57% (991) of reefs fall into the low and medium clusters (across all GCMs at the
GBRMPA management region scale), with many unable to maintain positive carbonate budgets
under future conditions. Partial dependence analysis revealed a range of depths from 10-15m
where the probability of a reef being clustered into the High cover cluster increased
substantially. Additionally, two-way partial dependence analysis revealed that high incoming
connectivity is important for High cluster assignment for reefs at depths of \>10m.
Considering this 10-15m depth range, and targetting well connected reefs, when assessing
possible intervention sites may reduce the exposure of planted and seeded corals to high
thermal stress, while still maintaining effective logistical access to sites. Managers are
also likely to consider the positive potential for flow on effects due to outgoing
connectivity when selecting intervention sites [@hock2017]. Within the context of reef
depth, reefs with high depths and high outgoing connectivity levels had the greatest
probability of being clustered into high cover clusters
(@sfig-ts-cluster-pdp-twoway-outgoing). These results suggests that interventions targetting
deep reefs will also benefit from high incoming and outgoing connectivity levels, allowing
for high potential for site resilience and outgoing flow of benefits and recovery.
Transient, and difficult to measure, properties such as reef connectivity are likely to
increase uncertainty in intervention planning to a greater degree than environmental
characteristics such as reef depth. Overall, reef intervention planning is a complex and
challenging decision-making process [@anthony2020], and our results suggest that
intervention site depth may be an important factor to additionally consider when assessing
the long-term resilience of sites.

It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
@torres2024]. Our results suggest that incoming connectivity contributes positively to high
cover cluster allocation for reefs over 10m deep. At depths of less than 10m thermal stress
may be too high for juveniles to contribute to long term recovery. While there is
interaction between incoming connectivity and depth for reef cluster prediction, according
to available input data, there are few reefs in the GBR that occur at depths \>10m and have
Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget),
resulting in overall low importance of connectivity as an individual feature for clustering
across the GBR. Furthermore, our results suggest no direct, first order, relationship
between weighted incoming connectivity and the ability of reefs to maintain positive
carbonate budgets under future conditions. There has been contrasting evidence [@bode2018;
@hock2017] surrounding whether recent generation connectivity modelling is able to identify
reefs that are important for recovery processes, with findings dependent on the larval
connectivity model used. These investigations were performed using prior generations of
larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018]
time periods, without considering the influence of reef depth on resilience. Using updated
1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample
of particle flows, our results suggest that larval connectivity alone may not be important
or reef resilience and recovery, but should be considered in combination with more
influential factors such as depth. In-depth comparisons and validation of multiple
connectivity model outputs would improve certainty and allow for the targetting of reefs by
combining abiotic factors such as depth with connectivity.

@@

Under all GCMs many reefs are projected to suffer substantial declines in coral cover
relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
lowest cover level cluster at the management area scale across GCMs. NorESM2-MM and
ACCESS-ESM1-5 GCMs convey the most coral cover maintenance into the future. Differences
between Low, Medium and High reef clusters in cover time series are most notable under these
two GCMs (@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into
the future is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of
future recovery and timespan of cover maintenance increase as GCM ECS increases
(@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
large declines and lower rates of recovery in high cover clusters are common compared to
lower-ECS GCMs.

@@

# Conclusion

@@

![Outgoing connection strength (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2060 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
lines within each violin represent the median base-10 log of outgoing connection strength
for each cluster and bands represent the distribution of connectivity values within each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_conn_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
fig-align="center" width="14.82cm"}

>>>>

---
title: Think deep for reef resilience
author:
  - name: Benjamin Grier
    email: grierben777@gmail.com
    affiliations:
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          state: QLD
    attributes:
        corresponding: true
  - name: Takuya Iwanaga
    email: t.iwanaga@aims.gov.au
    affiliations:
        - id: AIMS
          name: Australian Institute of Marine Science
          address: Cape Cleveland Rd
          city: Cape Cleveland
          state: QLD
    attributes:
        corresponding: true
abstract: |
    Coral reefs globally face unprecedented threats from climate change, with the Great Barrier
    Reef (GBR) experiencing cumulative stressors and increasingly severe declines in coral cover from thermal stress events.
    Understanding drivers behind reef resilience to climate impacts is critical for conservation
    planning and intervention strategies. A scenario-based population modelling approach was
    adopted with larval connectivity dynamics, thermal adaptation, and environmental factors
    to assess coral reef resilience across GBR locations under future climate projections.
    Using five Global Climate Models (GCMs) spanning five Equilibrium Climate Sensitivities,
    we analysed reef coral cover time series and the ability of reefs to maintain positive carbonate
    production budgets under future conditions. Contrary to expectations, larval connectivity
    patterns did not correlate with increases in maintenance of positive carbonate budgets.
    Instead, reef depth emerged as the primary predictor of cover-time series resilience and
    maintenance of positive carbonate budgets, with deeper reefs benefiting from thermal
    refugia that reduce bleaching impacts. Interaction between reef depth and incoming 
    connectivity was found to influence reef temporal behaviour. Our findings suggest that 
    depth provides critical protection against thermal stress, with high incoming connectivity enhancing the performance of deep reefs, contrasting current intervention
    practices that primarily target easily accessible sites in the 1-10m depth range. These results have 
    important implications for reef management, indicating that depth refugia should be 
    prioritized for further consideration in conservation planning alongside connectivity 
    considerations to maximize coral survival under continuing climate change.
keywords:
  - Coral reef
  - Climate change
  - Ecosystem resilience
  - Reef depth
  - Reef connectivity
date: last-modified
format:
  elsevier-docx:
    journal:
      name: Journal Name
      formatting: preprint
      cite-style: authoryear
bibliography: references.bib
engine: julia
crossref:
  custom:
  - kind: float
    reference-prefix: SFigure
    key: sfig
  - kind: float
    reference-prefix: STable
    key: stbl
editor:
  markdown:
    wrap: 92
    canonical: true
---

@@

Across bioregions there were no consistent patterns between reef clusters in mean DHW values
(@sfig-access-esm1-5-bioregion-dhwmean), Log-10 weighted incoming connectivity
(@sfig-access-esm1-5-bioregion-weightedincoming), Log-10 outgoing connection strength
(@sfig-access-esm1-5-bioregion-outgoingconn), Log-10 source-to-sink connectivity ratio
(@sfig-access-esm1-5-bioregion-logsosi) and Log-10 larval retention probability
(@sfig-access-esm1-5-bioregion-selfconn). Across six of the 29 bioregions reefs in the high
cover cluster have lower Log-10 carrying capacity values than reefs in other clusters
(@sfig-access-esm1-5-bioregion-carrying-capacity).

@@

Reef median depth had a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
@sfig-access-esm1-5-mean-carb-budget; @sfig-access-esm1-5-carb-budget-corr). Unsurprisingly,
the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as
does the Spearman's correlation (@sfig-access-esm1-5-carb-budget-corr). Decreasing
correlation levels are likely due to an increasing number of reefs being unable to maintain
coral cover above $\theta_0$ as it is increased, with the distribution of years above
threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In
contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no
correlation with the number of years a reef maintains cover above the required thresholds
(@sfig-access-esm1-5-carb-budget-corr).

@@

Reefs in different temporal clusters largely do not differ in mean modelled DHW levels
experienced and exhibit overall similar DHW time series. While reefs experience similar
magnitude DHWs based on SST, the proportion of a reefs' coral population impacted by heat
stress events depends on reef depth. Reefs at deeper depths are likely to be clustered into
High cover clusters. Reefs at shallow depths experience no, or few, years with coral cover
exceeding levels likely required to maintain positive carbonate budgets. Movement of shallow
reefs towards negative carbonate budgets in the future may contribute to phase shifts in
reef dominant CaCO~3~ production. Shifting from coral driven to encrusting algae driven
production, or to bioerosion dominated systems with rapid erosion of physical reef
frameworks [@dudgeon2010; @perry2008]. Reefs at increased depths may be able to maintain
coral driven CaCO~3~ production and accumulation into the future for longer. Our results
suggest that within shallow-water reef ecosystems (non-mesophotic, depth \< 30m), depth
contributes greatly to reef resilience and the ability of reefs to maintain positive
carbonate budgets under future conditions. Spatially our results indicate that regions of
positive carbonate budget maintenance, under ACCESS-ESM1-5, and high depth levels were
concentrated in the Far Northern, offshore Townsville/Whitsunday, and Mackay/Capricorn
management areas (@sfig-carb-budget-map; @sfig-depth-map). Resilient reefs in the Far
Northern management area were exposed to lower mean DHW levels than other reefs under
ACCESS-ESM1-5 (@sfig-mean-dhw-map), however similar spatial patterns were observed across
GCMs for reefs clustered into the high cover cluster category (@sfig-gcm-cluster-map). We do
not interpret these spatial findings as accurate predictions of future resilience due to
high uncertainty in input data, particularly depth and connectivity. While similar findings
have been demonstrated in the Pacific [@smith2014; @baird2018] and Indo-Pacific
[@bridge2014] regions, depth refugia analyses have often focussed on the potential of
mesophotic reefs (\> 30m deep) as thermal refugia [@bongaerts2010; @holstein2015;
@semmler2017]. In contrast, Venegas et al. [-@venegas2019] found no association between
depth and the alleviation of heat stress across a range of shallow reefs in the Pacific.

Our findings support the hypothesis that reefs at greater depths will exhibit
characteristics of refugia and more prolonged structural resilience under climate change
compared to shallower reefs. Additionally, Liu, Callaghan and Baldock [-@liu2024] suggest
that rubble instability is inversely correlated with reef depth, possibly limiting juvenile
coral recruitment capacity of shallow reefs. A caveat to our depth-resilience findings is
the quality of the bathymetry data used to calculate median reef depth. As detailed
previously, estimates of median reef depth are derived from satellite imagery (at $10m^2$
resolution) which can be subject to high degrees of uncertainty, both in terms of the
estimated depth for each pixel as well as their alignment to the established GBRMPA reef
outlines. Additionally, we do not incorporate light-based decreases in coral growth rates as
depth increases [@baker1975; @huston1985; @ruiz-diaz2022].

Current reef restoration and intervention efforts on the GBR, such as deployment of coral
seeding, coral fragment devices and Crown of Thorns Starfish control, target reefs with
sites in the 1-10m depth range [@howlett2021; @randall2021; @whitman2024]. While there are
no explicit justifications for this depth range, intervention depth is likely constrained by
snorkelling and diving deployment and monitoring logistical accessibility, visual
identification of sites from the surface, in combination with tourism return value. Our
results suggest that of the assessed reefs occurring within the 1-10m depth range (1736
reefs), 57% (991) of reefs are consistently clustered into the Low and Medium cover clusters
across the GCMs (at the GBRMPA management region scale), with many unable to maintain
positive carbonate budgets under future conditions. Partial dependence analysis revealed a
range of depths from 10-15m where the probability of a reef being clustered into the High
cover cluster increased substantially. Additionally, two-way partial dependence analysis
revealed that high incoming connectivity is important for High cluster assignment for reefs
at depths of \>10m. Considering this 10-15m depth range when assessing possible intervention
sites may reduce the exposure of planted and seeded corals to high thermal stress, while
still maintaining effective logistical access to sites. Managers are also likely to consider
the potential for positive flow on effects due to outgoing connectivity when selecting
intervention sites [@hock2017]. Two-way partial dependence analysis revealed reefs with high
depths and high outgoing connectivity levels have a high probability of being clustered into
more resilient reef clusters (@sfig-ts-cluster-pdp-twoway-outgoing). These results suggest
that interventions targetting deep reefs will also benefit from high incoming and outgoing
connectivity levels, allowing for high potential for site resilience and outgoing flow of
benefits and recovery. Transient, and difficult to measure, properties such as reef
connectivity are likely to increase uncertainty in intervention planning to a greater degree
than environmental characteristics such as reef depth. Overall, reef intervention planning
is a complex and challenging decision-making process [@anthony2020], and our results suggest
that intervention site depth may be an important factor to additionally consider when
assessing the long-term resilience of sites.

It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
@torres2024]. Our results suggest that incoming connectivity contributes positively to high
cover cluster allocation for reefs over 10m deep. At depths of less than 10m thermal stress
may be too high for incoming juveniles to contribute to long term recovery. While there is
interaction between incoming connectivity and depth for reef cluster prediction, according
to available input data, there are few reefs in the GBR that occur at depths \>10m and have
Log10 weighted incoming connectivity levels below 0 (@sfig-access-esm1-5-mean-carb-budget),
resulting in overall low importance of connectivity as an individual feature for clustering
across the GBR. Furthermore, our results suggest no direct, first order, relationship
between weighted incoming connectivity and the ability of reefs to maintain positive
carbonate budgets under future conditions. There has been contrasting evidence [@bode2018;
@hock2017] surrounding whether recent generation connectivity modelling is able to identify
reefs that are important for recovery processes, with findings dependent on the larval
connectivity model used. These investigations were performed using prior generations of
larval connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018]
time periods, without considering the influence of reef depth on resilience. Using updated
1km^2^ resolution larval connectivity across the whole GBR, with a limited temporal sample
of particle flows, our results suggest that larval connectivity alone may not be important
or reef resilience and recovery, but should be considered in combination with more
influential factors such as depth. Comprehensive comparisons and validation of multiple
connectivity model outputs would improve certainty and allow for the targetting of reefs by
combining abiotic factors such as depth with connectivity.

@@

Under all GCMs many reefs are projected to suffer substantial declines in coral cover
relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the Low
cover cluster at the management area scale across GCMs. NorESM2-MM and ACCESS-ESM1-5 GCMs
convey the most coral cover maintenance into the future. Differences between Low, Medium and
High reef clusters in cover time series are most notable under these two GCMs
(@stbl-cluster-cid; @fig-gcm-cover-trajectories). Maintenance of coral cover into the future
is linked to the Equilibrium Climate Sensitivity of the GCM used as levels of future
recovery and timespan of cover maintenance increase as GCM ECS increases
(@fig-gcm-cover-trajectories). Under high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2)
large declines and lower rates of recovery in high cover clusters are common compared to
lower-ECS GCMs.

@@

## Conclusion

@@

![Outgoing connection strength (in base-10 log scale) for reefs within each bioregion,
separated into clusters assigned by time series clustering. ‘Low’ clusters (green) are
clusters with the lowest median area-relative cover between 2030 and 2060 within each
bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative
cover between 2030 and 2060 within each bioregion. ‘High’ clusters (blue) are clusters with
the highest median area-relative cover between 2030 and 2060 within each bioregion. Solid
lines within each violin represent the median base-10 log of outgoing connection strength
for each cluster and bands represent the distribution of connectivity values within each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/bioregion/outgoing_strength_bioregion_violin.png){#sfig-access-esm1-5-bioregion-outgoingconn
fig-align="center" width="14.82cm"}
